---
title: "bio_task_eight"
output: html_document
date: "2023-06-12"
---

```{r setup, include=FALSE}
library(caret)
options(repos = c(CRAN = "https://cloud.r-project.org"))
# Install the kernlab package
install.packages("kernlab")
library(e1071)  # For Support Vector Machines (SVM)
```

## Load data and Remove rows with missing values


```{r}

load("C:/Users/USER/Downloads/breastcancer2.RData")
ls()
write.csv(dat, "test.csv")
breastcancer2  <- read.csv("test.csv")

breastcancer2 <- na.omit(breastcancer2)
head(breastcancer2, 5)
```

## Convert target variable to factor


```{r}
breastcancer2$y <- as.factor(breastcancer2$y)
```

## (a)
## Train a linear SVM

```{r}
linear_svm <- svm(y ~ ., data = breastcancer2, type = "C-classification", kernel = "linear", na.action = na.omit)
```

## Training accuracy

```{r}
train_acc <- sum(predict(linear_svm) == breastcancer2$y) / length(breastcancer2$y)
train_acc
```

## Cross-validated accuracy

```{r}
cv_acc <- train( y ~ ., data = breastcancer2, method = "svmLinear", trControl = trainControl(method = "cv", number = 10) )$results$Accuracy
cv_acc
```

## (b)
## Load the tree package

```{r}
library(tree)
```

## Construct the decision tree using tree

```{r}
classification_tree <- tree(y ~ ., data = breastcancer2, split = c("deviance","gini"), control = tree.control(nobs = nrow(breastcancer2), minsize = 5))
print(classification_tree)
plot(classification_tree)
text(classification_tree, pretty = 0)
```

## Obtain the training accuracy

```{r}
predicted <- predict(classification_tree, newdata = breastcancer2, type = "class")
training_accuracy <- mean(predicted == breastcancer2$y)
```

## Perform 10-fold cross-validation

```{r}
library(caret)
cv_results <- train(y ~ ., data = breastcancer2, method = "rpart", trControl = trainControl(method = "cv", number = 10))

```

## Result Accuracy for training tree  and 10 fold CV
```{r}
print(training_accuracy)
print(cv_results$results$Accuracy)
```

## (c)
## Using package randomForestSRC  instead of Ranger because of facing Installation problem with ranger.
```{r}
install.packages("randomForestSRC")
library(randomForestSRC)
```
## Convert  variables to factors and dataframe and check missing values

```{r}
breastcancer2 <- lapply(breastcancer2, as.factor)
breastcancer_df <- as.data.frame(breastcancer2)

# Check for missing values
if (any(is.na(unlist(breastcancer_df)))) {
  print("Dataset contains missing values. Handle missing values appropriately.")
  # Handle missing values in the dataset
  # ...
} else {
  print("No missing values found.")
}
```
##  Fit the classification model using randomForestSRC

```{r}
classification_model <- rfsrc(formula = y ~ ., data = breastcancer_df)
```
## Trainig accuracy  

```{r}
predicted_labels <- predict(classification_model, data = breastcancer_df)$predicted
predicted_labels
train_accuracy <- mean(predicted_labels == breastcancer_df$y)
```

## 10 fold CV
```{r}
cv_model <- rfsrc(formula = y ~ ., data = breastcancer_df, xbest = TRUE, nfold = 10)
```

## CV accuracy
```{r}
cv_predicted_labels <- cv_model$cvms$predicted
cv_accuracy <- mean(cv_predicted_labels == breastcancer_df$y)
```

